MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-25 paper.Rmd
Better refs for CRAN packages.

<!-- Define some macros to use later -->
[link-cran]:           https://cran.r-project.org
[link-ieatools]:       https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:        https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:            https://www.ilo.org/
[link-fao]:            https://www.fao.org/
[link-matsbyname]:     https://github.com/MatthewHeun/matsbyname
[link-matsindf]:       https://github.com/MatthewHeun/matsindf
[link-mwtools]:        https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfudatabase]:    https://github.com/energyeconomydecoupling/PFUDatabase
[link-pfuaggdatabase]: https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-rclabels]:       https://github.com/MatthewHeun/RCLabels
[link-recca]:          https://github.com/MatthewHeun/Recca
[link-targets]:        https://docs.ropensci.org/targets
[link-tidyverse]:      https://www.tidyverse.org

>>>>

<!-- Define some macros to use later -->
[link-cran]:           https://cran.r-project.org
[link-ieatools]:       https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:        https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:            https://www.ilo.org/
[link-fao]:            https://www.fao.org/
[link-matsbyname]:     https://CRAN.R-project.org/package=matsbyname
[link-matsindf]:       https://CRAN.R-project.org/package=matsindf
[link-mwtools]:        https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfudatabase]:    https://github.com/energyeconomydecoupling/PFUDatabase
[link-pfuaggdatabase]: https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-rclabels]:       https://CRAN.R-project.org/package=RCLabels
[link-recca]:          https://github.com/MatthewHeun/Recca
[link-targets]:        https://docs.ropensci.org/targets
[link-tidyverse]:      https://www.tidyverse.org
